Derive final annotations based on NBAtlas reference

### 2025-08-14 analyses/cell-type-neuroblastoma-04/final-annotation.Rmd
restore some changes i accidentally got rid of

Next, we compare labels across all three methods: if _two out of three_ methods agree, we assign the agreeing label.
Note that this requires mapping consensus cell types to NBAtlas labels, which is only possible for these cell types: endothelial cells, fibroblasts, and immune cell types except for the `NBAtlas` labels `RBCs` and `pDC` which do not have corresponding consensus labels.

@@

```{r fig.width = 10, fig.height = 10}
ggplot(umap_df) +
  aes(x = UMAP1, y = UMAP2, color = cell_type_assignment) +
  geom_point(alpha = 0.2, size = 0.3) +
  scale_color_manual(values = celltype_pal) +
  guides(color = guide_legend(override.aes = list(size = 2, alpha = 1), ncol=4))
```

>>>>

Next, we compare labels across all three methods: if at least _two out of three_ methods agree, we assign the agreeing label.
Note that this requires mapping consensus cell types to NBAtlas labels, which is only possible for these cell types: endothelial cells, fibroblasts, and immune cell types except for the `NBAtlas` labels `RBCs` and `pDC` which do not have corresponding consensus labels.

@@

```{r fig.width = 10, fig.height = 10}
ggplot(umap_df) +
  aes(x = UMAP1, y = UMAP2, color = cell_type_assignment) +
  geom_point(alpha = 0.2, size = 0.3) +
  scale_color_manual(values = celltype_pal) +
guides(color = guide_legend(override.aes = list(size = 2, alpha = 1)))
```
